\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-04 doc/paper.tex
note about tan(beta) resummation in Delta mb
add brief introduction to Section 5

\section{Stucture of the spectrum generator}
\label{Sec:SpecGenStruct}
\subsection{Model parameters and RGEs}

@@

and the \DRbar mass of the $\tau$ is calculated as

@@

\subsection{Tree-level spectrum}
The tree-level \DRbar masses are calculated by diagonalizing the mass
matrices returned from \code{SARAH`MassMatrix[]}.  The numerical
singular value decomposition is performed by the Eigen library routine
\code{Eigen::JacobiSVD} for matrices with less than four rows and
columns, and the LAPACK routines \code{zgesvd}, \code{dgesvd} for
larger matrices.  For the other types of diagonalization,
\code{Eigen::SelfAdjointEigenSolver} from Eigen is used regardless of
the matrix size.

@@

\subsection{Two-scale fixed point iteration}

@@

\subsection{Pole masses}
After the solver routine has finished and convergence has been
achieved, all $\overline{DR}$ parameters consistent with the
one-loop EWSB conditions, low energy data and all user supplied
boundary conditions are known at any scale between \code{LowScale} and
\code{HighScale}.

>>>>

\section{Structure of the spectrum generator}
\label{Sec:SpecGenStruct}

In this section we explain the internals of \fs's automatically
generated spectrum generator.
%
As mentioned in \secref{Sec:Program} one of \fs's design goals is to
create modular C++ code to allow for an easy exchange, extension and
reuse of the generated modules.  For this reason
\secref{Sec:ModelParametersAndRGEs} briefly describes the so-called
``model class'' hierarchy, which contains the general model
information, such as parameters, $\beta$-functions, \DRbar\ mass
spectrum, EWSB, self-energies, and the pole mass spectrum.
%
\secref{sec:boundary-conditions} describes how boundary conditions on
the model parameters are implemented in general at the C++ level.  The
subsections \ref{sec:calculation-of-gauge-couplings}--\ref{sec:ewsb}
explain how the parameters of the SUSY model are matched to the
Standard Model at the low scale and how the EWSB is imposed.
%
In \secref{sec:TreeLevelSpectrum} we describe the conventions used to
calculate the \DRbar\ mass spectrum.
%
In \secref{sec:TwoScaleFixedPointIteration} the algorithm which solves
the user-defined boundary value problem is described on the basis of
the CMSSM example given in \secref{Sec:modfile}.
%
Finally, \secref{Sec:PoleMasses} briefly summarizes how the pole mass
spectrum is obtained from the \DRbar\ model parameters after a
solution to the boundary value problem has been found.

\subsection{Model parameters and RGEs}
\label{Sec:ModelParametersAndRGEs}

@@

where $\tan\beta$ enhanced loop self-energy corrections are resummed.
Finally, the \DRbar mass of the $\tau$ is calculated as

@@

\subsection{Tree-level spectrum}
\label{sec:TreeLevelSpectrum}
The tree-level \DRbar masses are calculated by diagonalizing the mass
matrices returned from \code{SARAH`MassMatrix[]}.  The numerical
singular value decomposition is performed by the Eigen library routine
\code{Eigen::JacobiSVD} for matrices with less than four rows and
columns, and the LAPACK routines \code{zgesvd}, \code{dgesvd} for
larger matrices.  For the other types of diagonalization,
\code{Eigen::SelfAdjointEigenSolver} from Eigen is used regardless of
the matrix size.

@@

\subsection{Two-scale fixed point iteration}
\label{sec:TwoScaleFixedPointIteration}

@@

\subsection{Pole masses}
\label{Sec:PoleMasses}
After the solver routine has finished and convergence has been
achieved, all $\overline{DR}$ parameters consistent with the
one-loop EWSB conditions, low energy data and all user supplied
boundary conditions are known at any scale between \code{LowScale} and
\code{HighScale}.
